MLISA: Machine Learning-based \\ Intelligent Service Agents

### 2014-10-31 papers/webservice-coalition-learning/webservice_coalition_learning.tex
changes

In the last few years, communities of services have been studied in a certain numbers of proposals as virtual pockets of similar expertise. The motivation is to provide these services with high chance of discovery through better visibility, and to enhance their capabilities when it comes to provide requested functionalities. We introduce MLISA (Machine Learning-based Intelligent Service Agents) community framework that operates based on a trained model that regulates web service agents' decision making process in terms of cooperating with one another. This model uses the trained data in the form of information obtained from large number of web services regarding their single and cooperative utilities as well as environmental parameters such as demand, service quality, etc. The training model deploys logistic regression algorithm to build hypothesis function that can thoroughly address the aforementioned research problems. Our findings show that communities of web services can efficiently find the appropriate web service to invite cooperating with them as well as a single web service can find best communities to target joining them. In further details, after being trained, web services get to compute expectations as utilities they would gain while cooperating with communities of different characteristics. In contrast, communities can consider the training into account and analyze the characteristics of different individual web services and make prudent decisions while inviting a web service to join or accepting a join inquiry initiated from a web service. In general, MLISA equips web services with efficient methods of foreseeing how their choices of actions would impact their long-term and short-term goals, therefore opting for best decision available.

@@

In order to evaluate the performance of the mechanism we have used \emph{receiver operating characteristic} or \emph{ROC curve}, which is a graphical plot illustrating true positive rate against the false positive rate at various threshold settings in classifier systems. In order to be able to classify our communities strategy selection as correct or not, for each community we evaluated the training process by replacing the community in set with the closest one which its gets the strategy profile from. If actions are same and same utility levels are gained, we classify the decision as correct, otherwise its a wrong decision. The area under the \emph{ROC curve} called \emph{AUC} is equal to the probability that a classifier will rank a randomly chosen positive instance higher than a randomly chosen negative one\cite{xxx} and the higher number reflects better performance from the better solution.  Figure \ref{roc5} illustrates the \emph{ROC curve} evaluation of MLISA decision making mechanism. We compare our method with two other methods. The rational is based on assumption that communities as rational agents would join a community that increases their utility. And the greedy method only looks up the available list of communities and joins the one that maximizes its utility without considering any long term strategy or the other communities acceptance scenario. Figure \ref{roc5} compares the results for all these methods. The two other methods have very high failure rate compared to our method. Table \ref{fail_rate} illustrates the number of communities which failed to find the optimal and best collaboration group. The results prove the need of a long term training model for successful decision making process.

>>>>

abs

%In the last few years, communities of services have been studied in a certain numbers of proposals as virtual pockets of similar expertise. The motivation is to provide these services with high chance of discovery through better visibility, and to enhance their capabilities when it comes to provide requested functionalities. We introduce MLISA (Machine Learning-based Intelligent Service Agents) community framework that operates based on a trained model that regulates web service agents' decision making process in terms of cooperating with one another. This model uses the trained data in the form of information obtained from large number of web services regarding their single and cooperative utilities as well as environmental parameters such as demand, service quality, etc. The training model deploys logistic regression algorithm to build hypothesis function that can thoroughly address the aforementioned research problems. Our findings show that communities of web services can efficiently find the appropriate web service to invite cooperating with them as well as a single web service can find best communities to target joining them. In further details, after being trained, web services get to compute expectations as utilities they would gain while cooperating with communities of different characteristics. In contrast, communities can consider the training into account and analyze the characteristics of different individual web services and make prudent decisions while inviting a web service to join or accepting a join inquiry initiated from a web service. In general, MLISA equips web services with efficient methods of foreseeing how their choices of actions would impact their long-term and short-term goals, therefore opting for best decision available.

@@

In order to evaluate the performance of the mechanism we have used \emph{Receiver Operating Characteristic (ROC) curve}, which is a graphical plot illustrating true negative rate against the false positive rate at various threshold settings in classifier systems. In order to classify our communities' selection strategy correctly, for each community we evaluated the training process by replacing the community in set with the closest one, which it gets the strategy profile from. If actions are same and same utility levels are gained, we classify the decision as correct, otherwise its a wrong decision. The area under the \emph{ROC curve} called \emph{AUC} is equal to the probability that a classifier will rank a randomly chosen positive instance higher than a randomly chosen negative one\cite{xxx} and the higher number reflects better performance from the better solution.  Figure \ref{roc5} illustrates the \emph{ROC curve} evaluation of MLISA decision making mechanism. We compare our method with two other methods. The rational is based on assumption that communities as rational agents would join a community that increases their utilities. And the greedy method only looks up the available list of communities and joins the one that maximizes its utility without considering any long term strategy or the other communities acceptance scenario. Figure \ref{roc5} compares the results for all these methods. The two other methods have very high failure rate compared to our method. Table \ref{fail_rate} illustrates the number of communities which failed to find the optimal and best collaboration group. The results prove the need of a long term training model for successful decision making process.
